---
title: "Analysis Potential Customer Bank Portugal"
author : "Ana Sofia Noviandari"
date   : "April 5, 2021"
output: html_document
theme : yeti
highlight : espresso
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



```{r}
bank <- read.csv("bank-full.csv", sep = ";")
head(bank)
```

```{r}
str(bank)
summary(bank)

```
```{r}
library(ggplot2)
library(dplyr)
library(ggforce)
library(tidyverse)

```


```{r}
ggplot(data = bank, aes(x= age,))+
  geom_histogram(bins = 35, binwidth = 4, color = "black", fill = "maroon" )+
  labs(title="Customer Age Distribution",x="Age(years)", y = "Count",
       subtitle = "yellow line indicate average Age")+
  scale_x_continuous(breaks = seq(0,100,10))+
  geom_vline(xintercept = mean(bank$age), color = "yellow", linetype = 5)

```
```{r}
ggplot(bank, aes(x= marital, y = housing))+
  geom_col(fill= "blue")+
  ggtitle("Housing and Marital")
```


```{r}
ggplot(data = bank, aes(x=education))+
  geom_bar(fill = "dark blue")+ ggtitle("Subscription based on Education Level")+ 
  xlab(" Education Level")+
  guides(fill=guide_legend(title="Subscription of Term Deposit"))
```

```{r}
ggplot(bank, aes(x=duration, y=balance)) +
  facet_grid(cols = vars(y)) +
  geom_point(shape=1, color = "purple")+
  ggtitle("Duration VS Balance")
```



```{r}
bank %>% 
  group_by(education, job) 


ggplot(bank, aes(education, balance, fill = job ))+
  geom_bar(stat="identity", position = "dodge")+
  scale_fill_brewer(palette = "Paired")
  
  
```





```{r}
bank <- bank %>% 
  mutate(age_group=
      case_when(
      age > 20 & age <= 25 ~ "20-25",
      age > 25 & age <= 30 ~ "25-30",
      age > 30 & age <= 35 ~ "30-35",
      age > 35 & age <= 40 ~ "35-40",
      age > 40 & age <= 45 ~ "40-45",
      age > 45 & age <= 50 ~ "45-50",
      age > 50 & age <= 55 ~ "50-55",
      age > 55             ~ "above 55"
    )
  ) %>% 
   count(age_group, loan)

# calculate the start and end angles for each pie
bank_pies <- left_join(bank,
                      bank %>% 
                        group_by(age_group) %>%
                        summarize(n_total = sum(n))) %>%
  group_by(age_group) %>%
  mutate(end_angle = 2*pi*cumsum(n)/n_total,      # ending angle for each pie slice
         start_angle = lag(end_angle, default = 0),   # starting angle for each pie slice
         mid_angle = 0.5*(start_angle + end_angle))   # middle of each pie slice, for the text label

rpie = 1 # pie radius
rlabel = 0.6 * rpie # radius of the labels; a number slightly larger than 0.5 seems to work better,
                    # but 0.5 would place it exactly in the middle as the question asks for.ks for.
# draw the pies
ggplot(bank_pies) + 
  geom_arc_bar(aes(x0 = 0, y0 = 0, r0 = 0, r = rpie,
                   start = start_angle, end = end_angle, fill = loan)) +
  geom_text(aes(x = rlabel*sin(mid_angle), y = rlabel*cos(mid_angle), label = n),
            hjust = 0.5, vjust = 0.5) +
  coord_fixed() +
  scale_x_continuous(limits = c(-1, 1), name = "", breaks = NULL, labels = NULL) +
  scale_y_continuous(limits = c(-1, 1), name = "", breaks = NULL, labels = NULL) +
  facet_wrap(~age_group)+
  ggtitle("Loan By Age Group")

bank
```


```{r}
ggplot(bank, aes(x=age_group, y= balance, fill=age_group)) +
    geom_boxplot() +
    theme(
      plot.title = element_text(size=14), 
       ) +
    ggtitle("Balance by Age Group") +
    xlab("Years")+
    ylab("Balance")
```


#Conclusions

there is some insight that we can get from the plots:

1. Customers with married marital status has more tendencies to housing
2.  The Most Subscriptions Customers who have background secondary of education  level and the next position will be following by tertiary and then primary education levels
3. we can get the insight from plot Duration VS Balance:
  - The Customers with higher balance has shorter duration call to decides for subscription,
  - The Customers who have a smaller balance needs extended duration call to decide on subscription,
  - The Customers who do not want for a subscription they have shorter duration call then customers that going to say Yes to the subscription

4. The insight from the plot Balance, Job, and education level, that shows the customer with the highest balance has a job in management field with tertiary education level and the customer with the lowest balance who has a job as a student with primary education level

5. The last plot shows Segmentation of Loan Customers by Age,  Borrowers in Age Group 30-35 years is the highest group for the loan debt, And the second position of loan debt with adults aged 35 to 40, and the third position following by age 25-30 years old.

